Secure Composition \\ of Robust and Optimising Compilers \vspace{-1.5em}

### 2024-05-28 csf2/main.tex
compilation + intro 7

This section provides some additional formal insights into the case study. 
\Cref{subsec:formalities:props} demonstrates that the resulting projected security property using the universal image (\Cref{def:universal:img}) is faithful to the original property. 
\Cref{subsec:compatsecpasses} discusses a caveat with \Cref{thm:rtpsim:sig}, while \Cref{subsec:seccompproofs} gives some additional background on the secure compilation proofs that do not use the compositionality framework (\Cref{sec:sequential}).
Lastly, \Cref{subsec:formalities:maps} discusses a minor technicality related to the ``coloring'' of the investigated properties.

>>>>

This section provides additional insights for the formal development of the paper.
First, this section demonstrates that the security property resulting from the universal image projection is faithful to the original property (\Cref{subsec:formalities:props}). 
Then, it discusses why the order of compiler passes matters, and how does our framework help with identifying insecure compositions (\Cref{subsec:compatsecpasses}).
Finally, this section then gives additional technical insights on the secure compilation proofs (\Cref{subsec:seccompproofs}) and it discusses how to connect each language-specific security property to the general security properties presented in \Cref{sec:compprop} (\Cref{subsec:formalities:maps}).
